---
title: "流程控制及自訂函數-1"
author: "Nick"
date: "2020/1/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 流程控制

## if-else敘述
語法 :  if(condition) expr#1 else expr#2

```{r}
x<-6
if (x>5) y <- 2 else y <- 4
y

```

語法 : if(condition) {expr#1,...,expr#n } else {expr#1,...,expr#m}

```{r}
x<-6
y<-1
c<-0

if (x>5 && y <3){
    x<-x-1;
    y<-y+1;
  
}else{
    c<-3
}

x
y
c

```


語法 : if(condition) exp#1

```{r}
x<-6
if (x<10) y<-5
y
```

語法 : ifelse(condition,a,b)

```{r}

x<-6
y = ifelse (x<10,5,10) 
y

```


## if-else if-else敘述


```{r}
score<-70
if(score>=60){
  print("PASS")
}else if(score>=80){
  print("Good")
}else{
  print("Fail")
}
```



### <b> switch敘述</b>

語法 : switch(condition,expr#1,expr#2,...,expr#n)

```{r}
x<-1
switch(x,3,sum(1:5),sum(1:10))
x<-2
switch(x,3,sum(1:5),sum(1:10))
x<-3
switch(x,3,sum(1:5),sum(1:10))
x<-4
switch(x,3,sum(1:5),sum(1:10)) # 無回傳值


```


```{r}

y<-"meat"

switch(y,juice ="apple",meat="beef")

```


<br>

## <b>迴圈控制</b>

### <b>For Loop</b>

語法 : 

- for (index in expr#1) expr#2
- for (index in expr#1) {expr#2;...;expr#n}
```{r}
x <-0
for (i in 1:10) x<-x+i
x
```
```{r}
x<-0
y<-1
for (i in 1:10) {
  x<-x+i
  y<-y*x
}

x
y

```

### <b>While Loop</b>

語法 : 
- while (condition) expr#1
- while (condition) {expr#1;...;expr#m}

```{r}
sum <-0
i<-1
while(i<=10){
  sum <- sum+i;
  i<-i+1;
}

sum

```

### <b>Repeat & Break</b>
```{r}
sum <-0
i<-0
repeat{
  sum<-sum+1
  i<-i+1
  if (i>10)break
}
sum
```

### <b>Next</b>
```{r}
sum <-0

for (i in 1:50) {
  
if (i %% 2 == 0) next
    sum<-sum+1
}
sum

```

### <b>Apply</b>

語法 : apply(x,MARGIN,FUN,...)
- x 要執行的陣列或矩陣
- MARGIN value 1 = 列 ; 2 = 行
- FUN 為所欲執行的指定函數

```{r}
x<-array(1:24,dim = c(4,6))
x
```
```{r}
apply(x, 1, sum)
```
```{r}
apply(x, 2, sum)
```

